\documentclass[addpoints]{exam}


\pagestyle{headandfoot}
\firstpageheader{DOR}{First Exam}{July 4, 1776}
\runningheader{DOR}{First Exam}{\today}
\runningheadrule
\firstpagefooter{}{}{}
\runningfooter{DOR}{First Exam}{Page \thepage\ of \numpages}
\runningfootrule



\begin{document}


\noindent
\makebox[\textwidth]{Name:\enspace\hrulefill}

\vspace{0.25in}


\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering Answer the questions in the spaces provided on the question sheets.  If you run out of room for an answer, continue on the back of the page.}}}
\end{center}

\vspace{0.25in}


\centerline{Total Points: \numpoints}
\centerline{Total Questions: \numquestions}



\begin{center}
\gradetable[v][questions]
\end{center}

\newpage


\begin{questions}
\question[8]
\begin{parts}
\part[4]
How old is Dor Rondel?

\vspace{80px}

\part[4]
How old does Dor Rondel look?

\end{parts}

\vspace{110px}

\question[20]
\begin{parts}
\part[5]
Does Dor Rondel have a middle name?
\begin{oneparchoices}
\choice Yes
\choice No
\choice Maybe
\CorrectChoice Maybe
\end{oneparchoices}

\vspace{80px}

\part[5]
If so, what is it? (Write pass if he doesn't)

\vspace{80px}

\part[10]
What would be a good nickname for Dor Rondel?

\end{parts}

\newpage

\question[180] 
\begin{parts}
\part[30]
Describe Dor Rondel in a brief paragraph.

\vspace{180px}

\part[100]
What was your first impression of Dor Rondel?
\begin{choices}
\choice Ugly
\choice Pretty
\choice Average
\choice Model Status
\CorrectChoice Model Status
\end{choices}

\vspace{10px}

\part[50]
What do you think other people think of Dor Rondel?
\end{parts}

\newpage


\newpage


\question[3]
Did you like this test?
\begin{checkboxes}
\choice Yes
\choice No
\choice Not really
\choice Of course!
\CorrectChoice Of course!
\end{checkboxes}

\question[10]
Would you take this test again?
\begin{oneparcheckboxes}
\choice Yes
\choice No
\choice Not really
\choice Of course!
\CorrectChoice Of course!
\end{oneparcheckboxes}


\end{questions}

\end{document}
